---
title: "131 Homework2"
author: "Scott Shang (8458655)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

---
title: "131 Homework2"
author: "Scott Shang (8458655)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
---

```{r setup, echo=FALSE}
library(knitr)
# set global chunk options: images will be 7x5 inches
knitr::opts_chunk$set(fig.width=7, fig.height=5)
options(digits = 4)


## indents are for indenting r code as formatted text
## They may need to be adjusted depending on your OS
# if your output looks odd, increase or decrease indent
indent1 = '    '
indent2 = '        '
indent3 = '            '
```

Question1
```{r}
library("tidyverse")
library("tidymodels")
abalone=read_csv('abalone.csv')
head(abalone)
abalone$age=abalone$rings+1.5
head(abalone)
hist(abalone$age,breaks=20)
summary(abalone$age)
```
From the histogram above, we notice that the distribution of age is partially normal distributed, but slightly skewed to the right, with minimum 2.5, maximum 30.5, and mean 11.4. 

Question2
```{r}
set.seed(1234)
ab_split=initial_split(abalone,prop=0.80,strata=age)
ab_train=training(ab_split)
ab_test=testing(ab_split)
```


Question3
```{r}
ab_recipe=recipe(age~type+longest_shell+diameter+height+whole_weight+shucked_weight+viscera_weight+shell_weight,data=ab_train)%>%
  step_dummy(all_nominal_predictors())%>%
  step_interact(terms=~type_I:shucked_weight+type_M:shucked_weight+longest_shell:diameter+shucked_weight:shell_weight)%>%
  step_normalize(all_predictors())

```
We shouldn't use rings to predict age because age is depends on age, so we won't have the relation between age and other predictors.

Question4
```{r}
lm_model=linear_reg()%>% 
  set_engine("lm")
```


Question5
```{r}
lm_wflow=workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(ab_recipe)
```


Question6
```{r}
lm_fit=fit(lm_wflow,ab_train)

ab_test=data.frame("type"="F","longest_shell" = 0.50, "diameter" = 0.10, "height" = 0.30, "whole_weight" = 4, "shucked_weight" = 1, "viscera_weight" = 2, "shell_weight" = 1)

predict(lm_fit,new_data=ab_test)
```


Question7
```{r}
ab_metric=metric_set(rsq,rmse,mae)
ab_pred=predict(lm_fit,new_data=ab_train%>%select(-age))
ab_pred=bind_cols(ab_pred,ab_train%>%select(age))
ab_pred

ab_metric(ab_pred,truth=age,estimate=.pred)
```
The R-squared value we got is 0.55. It's a measure of how much variation of the response variable is explained by the predictors. In this case, we found that our model is not that good. 
